### 2017-04-02 paper/modes.tex
pass on modes.tex

The list below shows the choices to control parallelism within a Java
virtual machine (JVM) which runs in a single process of the CPU.

\begin{itemize}
\item
    \textbf{Sequential (\Seq).}~No parallelism is involved.
\item
    \textbf{Sequential classes; parallel methods
        (\SeqClassParMeth).}~This configuration corresponds to the
        sequential execution of test classes and test methods run in
        multiple threads.
\item
    \textbf{Parallel classes; sequential methods
        (\ParClassSeqMeth{}).}~This configuration corresponds to the
        execution of test classes in multiple threads and tests run
        sequentially within each thread.
\item
    \textbf{Parallel classes; Parallel methods
        (\ParClassParMeth).}~This configuration corresponds
        conceptually to the union of \ParClassSeqMeth{} and
        \SeqClassParMeth{}: the testing framework runs test methods
        from several classes on multiple threads.
\end{itemize}

The configuration \Seq{} is a proper fit for short-running test suites
since this is the default configuration and the execution provides
feedback in an acceptable time. However, for costly suites, it is
impractical for developers to wait long-running executions to take
action.  In this scenario, the remaining configuration may help to
amortize the execution cost depending on how the test suite was
designed. For instance, the configuration \SeqClassParMeth{} may
speedup the execution of test suites composed large test classes since
the cost of running all test methods is amortized by a pool of
threads. Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several small test classes. Notice that both
configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
data-race condition at different levels. For instance, if two test methods performs operations in a same variable, the configuration \SeqClassParMeth{} would be preferable. Finally, 
the configuration \ParClassParMeth{} does not impose any sequential 
execution but it is more likely to manifest data-races as methods 
from different classes run in parallel.

>>>>

The list below shows the choices to control parallelism within one
Java virtual machine (JVM), which runs in a single CPU process.  These
options are offered by the testing framework, \eg{}, JUnit.

\begin{itemize}
\item
    \textbf{Sequential (\Seq).}~No parallelism is involved.
\item
    \textbf{Sequential classes; parallel methods
      (\SeqClassParMeth).}~This configuration corresponds to running
    test classes sequentially, but running test methods from those
    classes concurrently.
\item
    \textbf{Parallel classes; sequential methods
      (\ParClassSeqMeth{}).}~This configuration corresponds to running
    test classes concurrently, but running test methods sequentially.
\item
    \textbf{Parallel classes; Parallel methods
      (\ParClassParMeth).}~This configuration corresponds to the
    combination of \SeqClassParMeth{} and \ParClassSeqMeth{}.  
\end{itemize}

%% The configuration \Seq{} is a proper fit for short-running test suites
%% since this is the default configuration and the execution provides
%% feedback in an acceptable time. However, for costly suites, it is
%% impractical for developers to wait long-running executions to take
%% action.  In this scenario, the remaining configuration may help to
%% amortize the execution cost depending on how the test suite was
%% designed. For instance,

Notice that an important aspect in deciding which configuration to use
(or in designing new test suites) is the possibility of race
conditions on shared data during execution. For instance,
configuration \ParClassSeqMeth{} may be preferable over
\SeqClassParMeth{} when it is clear that several test methods in one
class perform operations involving one given variable that is visible
statically or within the scope of the test class.

\Fix{unconvincing.  please, revise this.$\rightarrow$}Considering efficiency, the
configuration \SeqClassParMeth{} may speedup the execution of test
suites composed of large test classes since the cost of running all
test methods is amortized by a pool of threads\Mar{$\leftarrow$
  unclear to me.  you need to argument why one would prefer C1 over
  C2.}. Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several small test classes.\Mar{$\leftarrow$
  again, unclear to me (the reader).}  Finally, the configuration
\ParClassParMeth{} does not impose any sequential execution but it is
more likely to manifest data-races as methods from different classes
run in parallel.
